\cvsection{Experiência}
\begin{cventries}
    \cventry
    {Cientista de Dados}
    {Wildlife Studios}
    {São Paulo, Brazil}
    {Dec. 2021- Present}
    {
      \begin{cvitems}
        \item {Supported the biggest company game, Sniper 3D (1MM active players/day), interacting directly with executive stakeholders to make data driven business decisions. }
        \item {Conducted A/B tests to evaluate the effectiveness of different business strategies for revenue growth and retention improvement. }
        \item {Developed KPI dashboards, including calculated error bars and variance reduction techniques to reduce statistical uncertainty. }
        \item {Developed a recommendation engine using collaborative filtering algorithms to replace a random policy in the gacha of Zooba to give players the character they would most likely enjoy playing with. }
        \item {Performed Data Collection and maintained Machine Learning and Reinforcement Learning models for offer optimization.}
        \item {Provided ad hoc analyses and data investigations followed by detailed reports and documentation, that helped understand the causes of underperformance in the game KPIs. }
        \item {Generated insights through data analysis to identify improvements in the game's onboarding and matchmaking experience. }
        \item {Worked with SQL and PySpark to extract and manipulate data containing user events. }
        \item {Used R's ggplot2 for clean, high-quality and customizable data visualization. Also worked with Looker for dashboard creation and data exploration. }
        \item {Collaborated with Data Engineering team to develop treated tables with business rules. }
        \item {Demonstrated  strong verbal and written communication skills in an international environment. }
      \end{cvitems}
    }
    \cventry
    {Cientista de Dados}
    {Itaú Unibanco}
    {São Paulo, Brasil}
    {Jul. 2020- Presente}
    {
      \begin{cvitems}
        \item {Realização de projetos de aprendizado supervisionado e não supervisionado para áreas de negócios. }
        \item {Desenvolvimento de cases de Retenção, Precificação e Lifetime Value. }
        \item {Ministração de monitorias e treinamentos, passando por tópicos de Regressão, Classificação e Agrupamento. }
      \end{cvitems}
    }

    \cventry
    {Cientista de Dados}
    {Banco PAN}
    {São Paulo, Brasil}
    {Jul. 2019- Jul. 2020}
    {
      \begin{cvitems}
        \item {Desenvolvimento de modelos e políticas de concessão e manutenção de crédito. }
        \item {Modelos de Machine Learning para probabilidade de default. }
      \end{cvitems}
    }

    \cventry
    {Cientista de Dados}
    {Dotz (Programa de fidelidade)}
    {São Paulo, Brasil}
    {Jul. 2018 - Jul. 2019}
    {
      \begin{cvitems}
        \item {Realização de projetos envolvendo análises estatísticas e algoritmos de Machine Learning. }
        \item {Desenvolvimento de modelos de Sistemas de Recomendação, Elasticidade de Preço e Classificação de Perfil de clientes. }
      \end{cvitems}
    }

    \cventry
    {Desenvolvimento iOS}
    {Apple Developer Academy | Instituto Eldorado}
    {Campinas, Brasil}
    {Jul. 2017 - Dez. 2018}
    {
      \begin{cvitems}
        \item {Desenvolvimento de aplicativos com a linguagem orientada a objetos Swift.}
      \end{cvitems}
    }

    \cventry
      {Iniciação Científica}
      {PIBIC - CNPq}
      {Campinas, Brasil}
      {Jul. 2016 - Jul. 2018}
      {
        \begin{cvitems}
          \item {Estruturação de banco de dados climáticos usando ArcGIS, Python e R}
        \end{cvitems}
      }
% \end{cventries}
% \cvsubsection{Open Source Projects}
% \begin{cventries}
%   \cventry
%     {Definition and Implementation of the V language}
%     {V Language}
%     {}
%     {}
%     {}
%   \cventry
%     {Visual Java application to simulate gravitation interaction between multiple bodies}
%     {N-Body Simulator}
%     {}
%     {}
%     {}
%   \cventry
%     {Java application to visually find the largest clique and independent set in a graph}
%     {Clique and Independent Set Finder}
%     {}
%     {}
%     {}
\end{cventries}
