\cvsection{Experience}
\begin{cventries}

    \cventry
    {Data Scientist}
    {Wildlife Studios}
    {São Paulo, Brazil}
    {Dec. 2021- Present}
    {
      \begin{cvitems}
        \item {Supported the biggest company game, Sniper 3D (1M+ active players/day), interacting with executive stakeholders to make data driven business decisions, directly impacting in the game's economy and monetization. }
        \item {Conducted A/B tests to evaluate the effectiveness of different business strategies for revenue growth and retention improvement. }
        \item {Developed KPI dashboards, including estimate confidence intervals and CUPED to reduce statistical uncertainty. }
        \item {Developed a recommendation engine using collaborative filtering algorithms to replace a random policy in the gacha of Zooba to give players the character they would most likely enjoy playing with. }
        \item {Acted as a maintainer for a Machine Learning product for offer optimization, contributing to 10\% of the total in-app purchases revenue. This involved designing experiments, collecting data, developing models, deploying them to production, and monitoring the results of Reinforcement Learning, Supervised Learning, and Heuristics models. }
        \item {Provided ad hoc analyses and data investigations followed by detailed reports and documentation, that helped understand the causes of underperformance in the game KPIs. }
        \item {Generated insights through data analysis to identify improvements in the game's onboarding and matchmaking experience. }
        \item {Worked with SQL and PySpark to extract and manipulate data containing user events. }
        \item {Used R's ggplot2 for clean, high-quality and customizable data visualization. Also worked with Looker for dashboard creation and data exploration. }
        \item {Collaborated with Data Engineering team to develop treated tables with business rules. }
        \item {Demonstrated  strong verbal and written communication skills in an international environment. }
      \end{cvitems}
    }

    \cventry
    {Data Scientist}
    {Itaú Unibanco}
    {São Paulo, Brazil}
    {Jul. 2020- Nov. 2021}
    {
      \begin{cvitems}
        \item {Assisted different areas in the bank (Credit card, Payroll, Loan) with Data Science projects involving supervised and unsupervised learning. }
        \item {Experience with Retention, Pricing and Lifetime Value problems, using Python's Machine Learning frameworks. }
        \item {Conducted study groups and training sessions for aspiring Data Scientists with topics on Regression, Classification and Clustering techniques. }
      \end{cvitems}
    }

    \cventry
    {Data Scientist}
    {Banco PAN}
    {São Paulo, Brazil}
    {Jul. 2019- Jul. 2020}
    {
      \begin{cvitems}
        \item {Built Machine Learning Models for probability of default, including scorecards, logistic regression models and Gradient Boosting. }
        \item {Leveraged visualizations as a tool for communicating results, introducing SHAP Values to extract feature importance and explain black-box models. }
        \item {Created various new variables using Feature Engineering to improve performance of existing models. }
      \end{cvitems}
    }

    \cventry
    {Data Scientist}
    {Dotz (Loyalty program)}
    {São Paulo, Brazil}
    {Jul. 2018 - Jul. 2019}
    {
      \begin{cvitems}
        \item {Worked on several projects of personalization using statistical models and business concepts.}
        \item {Built a Recommender System using Collaborative Filtering using transactional data of shoppers.}
        \item {Used Price Elasticity techniques to identify products that are more sensitive for discounts.}
      \end{cvitems}
    }

    \cventry
    {iOS Development}
    {Apple Developer Academy | Instituto Eldorado}
    {Campinas, Brazil}
    {Jul. 2017 - Dec. 2018}
    {
      \begin{cvitems}
        \item {App development using object oriented programming with Swift and project management with Agile SCRUM.}
      \end{cvitems}
    }

    \cventry
      {Scientific Initiation}
      {PIBIC - CNPq}
      {Campinas, Brazil}
      {Jul. 2016 - Jul. 2018}
      {
        \begin{cvitems}
          \item {Data Collection using Web Scraping of climatic data using R and worked with raster files in ArcGIS.}
        \end{cvitems}
      }
% \end{cventries}
% \cvsubsection{Open Source Projects}
% \begin{cventries}
%   \cventry
%     {Definition and Implementation of the V language}
%     {V Language}
%     {}
%     {}
%     {}
%   \cventry
%     {Visual Java application to simulate gravitation interaction between multiple bodies}
%     {N-Body Simulator}
%     {}
%     {}
%     {}
%   \cventry
%     {Java application to visually find the largest clique and independent set in a graph}
%     {Clique and Independent Set Finder}
%     {}
%     {}
%     {}
\end{cventries}